Continuous Generalization of Buildings by Growing and Merging

### 2017-09-04 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
finished the description of figures/RemoveBay.pdf

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{}
	\label{fig:Buffer_MiterLimits}
\end{figure*}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure*}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Uniting}
	\caption{Unite a polygon with the polygon at the immediately previous step.
		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
	}
	\label{fig:Shrink_Uniting}
\end{figure}

@@

\subsection{Group buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
the corresponding two buildings will become too close at time $t$.
As a result, the two buildings are identified as in the same group.

@@

>>>>

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{}
	\label{fig:Buffer_MiterLimits}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Uniting}
	\caption{Unite a polygon with the polygon at the immediately previous step.
		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}c and the 
		polygon of \fig\ref{fig:Shrink_Erosion}g;
		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}c and 
		the polygon of \fig\ref{fig:Shrink_Simplification}h;
	}
	\label{fig:Shrink_Uniting}
\end{figure}

@@

\subsection{Group buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings 
(see \fig\ref{fig:RemoveBay} for example). 
We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
the corresponding two buildings will become too close at time $t$.
As a result, the two buildings are identified as in the same group.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
		(d) Dilate the polygons in (c) with distance 
		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
		If two polygons in (d) intersect, 
		the original buildings in (a) will be put in the same group 
		because they will become too close at time $t$.
		Until this step, there two groups according to (d), 
		one consists of the single middle building and 
		the other group consists of the surrounding $9$ buildings.
		The process of (e), (f), and (g) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		There is only one group left according to (g).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	\label{fig:RemoveBay}
\end{figure*}
